---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Author Name"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "California State University, Northridge"

abstract: |

  help found here --> https://bit.ly/3Npz1e7
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Place discussion here, just below the title of the project. Notice that Methods, Results, References and Appendices begin in a new page. Visit this link to learn how to write an Introduction section: https://bit.ly/3C46nbw

Please, do not change the font size or type.

\newpage

# Methods

  Help found here --> https://bit.ly/3iAR2rQ

## Participants

  Help found here --> https://bit.ly/3iAR2rQ

## Design

  Help found here --> https://bit.ly/3iAR2rQ
  More help found here --> https://bit.ly/37TZdgE

## Statistical analysis

  Help found here --> https://bit.ly/31skJ5I

## Materials

  Help found here --> https://bit.ly/3iAR2rQ

## Procedures

  Help found here --> https://bit.ly/3iAR2rQ
  
\newpage

# Results

  Help found here --> https://bit.ly/3Lg9qT5

\newpage

# References

  Help found here --> https://bit.ly/3tHqIm7

\newpage
  
# Appendices

Add here the preliminary info turned in previously

