---
title: "Chapter 07: Fundamentals of Inferential Statistics"
subtitle: "⚔<br/>Introduction to Statistics in Kinesiology"
author: "Furtado JR., O"
institute: "Cal State Northridge"
date: "updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
---

```{r broadcast, echo=FALSE}
xaringanExtra::use_broadcast()
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```
```{r xaringan-editable, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```
```{r style-share-again, echo=FALSE}
xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin")
)
```
```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r xaringan-tachyons, echo=FALSE}
xaringanExtra::use_tachyons()
```
```{r}
xaringanExtra::use_webcam()
```

```{r xaringanExtra-search, echo=FALSE}
xaringanExtra::use_search(show_icon = TRUE)
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```


# From sample to population
## - Inferential statistics: the process of estimating population parameters based on sample statistics.
### 1. Difficult to access entire population
### 2. Population estimation is made based on sample

Statistic > Parameter

---
# Parameter vs Statistic

*Parameter* is a characteristic of the population, while *stastistic* is an estimate of a parameter based on the information obtained from a sample.

| Measurement               | statistics    | parameter |
| :---  | :----: | :----:   |   :----:      |
| Population Proportion     | p             | P         |
| Data points               | x             | X     |
| Population mean           | $\bar{x}$     | $\mu$|
| Standard deviation        | s           | $\sigma$|
| Variance                  | s<sup>2 | $\sigma$<sup>2   |
| Number of persons/objects | n             | N|
| Correlation coefficient   | *r*            | $\rho$|

Also:

H<sub>0</sub>: for **null hypothesis**

H<sub>1</sub>: for **alternate hypothesis**

---
# Sampling error

## the amount of error in the estimate of a population parameter
## Standard error of the mean (*SE<sub>m</sub>*)

$$\sigma_{\bar{X}} = \frac{s}{\sqrt{N}}$$

(*SE<sub>m</sub>*) = estimate of the amount of error when a sample mean ( $\bar{x}$ ) is used to estimate the population mean ( $\mu$ ).

Since the $\mu$ cannot be known, we use the $\bar{x}$ and a estimate of the error (*SE<sub>m</sub>*) we should to expect. 

---
# LOC and Probability error
## Levels of confidence (LOC)
- A percentage value that establishes the probability that a statement is correct

## Probability error
**Common values**:
- at 68% LOC, probability of error = 32%
- at 90% LOC, probability of error = 10%
- at 95% LOC, probability of error = 5%

---
# Hypothesis testing





.panelset[
.panel[.panel-name[even]

| id    | scores |
| :---  | :----: |
| 1     |   2   |
| 2     |   4  |
| 3     |   7  |
| 4     |   11  |
| 5     |   12  |
| 6     |   14  |
]
.panel[.panel-name[odd]

| id    | scores |
| :---  | :----: |
| 1     |   2   |
| 2     |   4  |
| 3     |   7  |
| 4     |   11  |
| 5     |   12  |
| 6     |   14  |
| 7     |   16  |
]
]

---
# Median, cont.
## - Represents the score at the **50th percentile**

--
## - Divides the data set in two (visible in a boxplot)

--
## - If *N* is odd, **median** is the middle score<sup>1</sup> 

--
## - If *N* is even, do one of the following:
- Use the higher of the two middle scores
- Compute the average of the two middle scores


.footnote[
[1] data must be ranked first.
]

---
# Median (cont.)
## When to use the **median**?

### - use with ordinal data or cases of highly skewed distributions

--
### Important: not affected by extreme scores

---
# Mean 

### The **mean**<sup>1</sup> is the most popular index of central tendency

#### Equation for the **sample** mean:
\begin{align} \bar{x}=\frac{\sum x}{n} \end{align}

#### Equation for the **population** mean:
\begin{align} \mu=\frac{\sum x}{N} \end{align}

.footnote[
[1] equal to arithmetic average
]

---
# Mean (cont.) 

## The most sensitive of the central tendency indices
### 1. affected by every score in the
### 2. greatly affected by outliers

--
## Play important role on statistical inference

--
## Used with interval and ratio data<sup>1</sup>

.footnote[
[1] In `jamovi`, interval and ratio = **continuous** data
]

---
# Test

.panelset[
.panel[.panel-name[tab1]
content tab1
]
.panel[.panel-name[tab2]
content tab2
]
]




