---
title: "Chapter 04 - Measures of Central Tendency"
subtitle: "⚔<br/>Introduction to Statistics in Kinesiology"
author: "Furtado JR., O"
institute: "Cal State Northridge"
date: "updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, tamu, tamu-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
---

```{r broadcast, echo=FALSE}
xaringanExtra::use_broadcast()
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```
```{r xaringan-editable, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```
```{r style-share-again, echo=FALSE}
xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin")
)
```
```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r xaringan-tachyons, echo=FALSE}
xaringanExtra::use_tachyons()
```
```{r}
xaringanExtra::use_webcam()
```

```{r xaringanExtra-search, echo=FALSE}
xaringanExtra::use_search(show_icon = TRUE)
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```


# Mode
## - The most frequent or common score in a distribution

--
## - What if more than one mode?

--
Bimodal, trimodal... multimodal

--
## Disadvantages

--
### 1. Not useful for further calculations
### 2. not affected by extreme scores (outlines)

---
# Median


.panelset[
.panel[.panel-name[even]

| id    | scores |
| :---  | :----: |
| 1     |   2   |
| 2     |   4  |
| 3     |   7  |
| 4     |   11  |
| 5     |   12  |
| 6     |   14  |
]
.panel[.panel-name[odd]

| id    | scores |
| :---  | :----: |
| 1     |   2   |
| 2     |   4  |
| 3     |   7  |
| 4     |   11  |
| 5     |   12  |
| 6     |   14  |
| 7     |   16  |
]
]

---
# Median, cont.
## - Represents the score at the **50th percentile**

--
## - Divides the data set in two (visible in a boxplot)

--
## - If *N* is odd, **median** is the middle score<sup>1</sup> 

--
## - If *N* is even, do one of the following:
- Use the higher of the two middle scores
- Compute the average of the two middle scores


.footnote[
[1] data must be ranked first.
]

---
# Median (cont.)
## When to use the **median**?

### - use with ordinal data or cases of highly skewed distributions

--
### Important: not affected by extreme scores

---
# Mean 

### The **mean**<sup>1</sup> is the most popular index of central tendency

#### Equation for the **sample** mean:
\begin{align} \bar{x}=\frac{\sum x}{n} \end{align}

#### Equation for the **population** mean:
\begin{align} \mu=\frac{\sum x}{N} \end{align}

.footnote[
[1] equal to arithmetic average
]

---
# Mean (cont.) 

## The most sensitive of the central tendency indices
### 1. affected by every score in the
### 2. greatly affected by outliers

--
## Play important role on statistical inference

--
## Used with interval and ratio data<sup>1</sup>

.footnote[
[1] In `jamovi`, interval and ratio = **continuous** data
]

---
# Test

.panelset[
.panel[.panel-name[tab1]
content tab1
]
.panel[.panel-name[tab2]
content tab2
]
]




